Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-04-27 ms.tex
added a tetrahedral/zincblende projection that matches detector angles.
more on the zincblende bond structure.

\subsection{Subpixel Crosshatching}
The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
The angle between these lines is thus 44.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
\caption{
The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
}\label{fig:crossHatchA5}
\end{figure}

>>>>

\subsection{Subpixel Crosshatching}
The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
The angle between these lines are 67.60$\degree$, 44.5$\degree$ and 67.8$\degree$.
These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.

The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
We therefore conclude that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
\caption{
The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
}\label{fig:crossHatchA5}
\end{figure}
